\vspace{-2.5em} Singular value decomposition of a dual\\ orthogonal-view fluorescence microscope\vspace{-1em}

### 2018-06-08 notes/2018-05-31-dispim-svd/report/report.tex
Tikhonov regularization for plain diSPIM.

A potentially useful result is to decompose the Moore-Penrose pseudoinverse
operator
\begin{align}
  \mc{H}^+g_{\text{v}}(\rd{}) = \frac{1}{\sigma_{\bs{\rho}}}\mb{u}\mb{v}^{\dagger}g_{\text{v}}(\rd{}) = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}\frac{H_{\text{v}}(\bs{\rho})}{H_{\text{A}}^2(\bs{\rho}) + H_{\text{B}}^2(\bs{\rho})}\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}. \label{eq:mp}
\end{align}
This gives us a (new?) one-step reconstruction algorithm. In words:
\begin{enumerate}
\item Calculate or measure the kernel and transfer function of the microscope
  for both views and precalculate two filters:
  $H_{\text{A}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$ and $H_{\text{B}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$.
\item Take the 3D Fourier transform of the data from each view, multiply the
  result by the corresponding precalculated filter from step 1, then add the
  results.
\item Take the inverse Fourier transform. 
\end{enumerate}
This reconstruction is fast---it only requires three 3D Fourier transforms and a
single product---so it might be useful for live reconstructions during imaging.

@@

>>>>

A potentially useful result is to decompose the Moore-Penrose pseudoinverse
operator
\begin{align}
  \mc{H}^+g_{\text{v}}(\rd{}) = \frac{1}{\sigma_{\bs{\rho}}}\mb{u}\mb{v}^{\dagger}g_{\text{v}}(\rd{}) = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}\frac{H_{\text{v}}(\bs{\rho})}{H_{\text{A}}^2(\bs{\rho}) + H_{\text{B}}^2(\bs{\rho})}\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}. \label{eq:mp}
\end{align}
This gives us a (new?) one-step reconstruction algorithm. In words:
\begin{enumerate}
\item Calculate or measure the kernel and transfer function of the microscope
  for both views and precalculate two filters:
  $H_{\text{A}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$ and $H_{\text{B}}(\bs{\rho})/[H^2_{\text{A}}(\bs{\rho}) + H^2_{\text{B}}(\bs{\rho})]$.
\item Take the 3D Fourier transform of the data from each view, multiply the
  result by the corresponding precalculated filter from step 1, then add the
  results.
\item Take the inverse Fourier transform. 
\end{enumerate}
This reconstruction is fast---it only requires three 3D Fourier transforms, two
scalings, and a sum---so it might be useful for live reconstructions during
imaging.

@@

\section{Tikhonov regularization}
The pseudoinverse solution amplifies high-frequency noise, so we prefer a
one-step algorithm with Tikhonov regularization. Barrett 15.114 (and discussion
around 15.155 and 1.5156) gives the Tikhonov regularized reconstruction operator
as
\begin{align}
  \mc{H}^{+\text{Tik}}_{\eta}[g_{\text{v}}(\rd{})] = \frac{\sigma_{\bs{\rho}}}{\sigma^2_{\bs{\rho}} + \eta}\mb{u}\mb{v}^{\dagger}[g_{\text{v}}(\rd{})] = \mc{F}^{-1}\left\{\sum_{\text{v} = \{\text{A}, \text{B}\}}\frac{H_{\text{v}}(\bs{\rho})}{H_{\text{A}}^2(\bs{\rho}) + H_{\text{B}}^2(\bs{\rho}) + \eta}\mc{F}\left\{g_{\text{v}}(\ro{})\right\}\right\}.
\end{align}
The Tikhonov regularized solution is identical to the pseudoinverse solution when $\eta = 0$ as expected.
